Eviction and Crime: Evidence from Boston

### 2023-04-12 writing/paper/main.tex
Updates from Overleaf

@@

    \subsection{Crime Incidents Data}
    I obtain incident-level records of every crime incident to which BPD offers responded to from August 2015 to present. Each record includes the a date, latitude and longitude coordinates, and an offense code indicating the type of crime incident that occurred. I drop all records missing any of these three variables.

    \subsection{Census Tract Characteristics Data}
    I obtain time-invariant census tract level characteristics of the properties in my sample from Opportunity Insights \citep{chetty_impacts_2018}. This data includes information such as population density, job density, median household income, and poverty rate. Figure 2 plots the locations of the evictions in my sample, coloring Boston's census tracts according to their poverty rates. It shows that the density of eviction filings tends to be higher in poor areas. This result is consistent with existing research that finds strong associations between poverty and the prevalence of eviction \citep{desmond_housing_2016}. Indeed, <>, mirroring the findings of \cite{collinson_eviction_2022} in New York City and Chicago.

            \begin{figure}[H]
            \centering
            \includegraphics{output/summary_statistics/figures/evictions_map.png}
            \caption{Spatial Incidence of Eviction}
            \label{fig:my_label}
        \end{figure}

@@

    Table 1 contains descriptive statistics for the panel dataset.

@@

\section{Results and Mechanisms} \label{sec:result}

    \subsection{D.R. Estimates of the ATT}
    \begin{figure}[H]
        \centering
        \includegraphics{output/group_0_crimes_500m/figures/att_gt_dr_event_study_long_horizon.png}
        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters}
        \label{fig:my_label}
    \end{figure}

@@

>>>>

\begin{table}[H]
    \centering
    \input{output/summary_statistics/tables/sample_restriction}
    \caption{Sample Construction}
    \label{tab:my_label}
\end{table}

@@

    \subsection{Crime Incidents Data}
    I obtain incident-level records of every crime incident to which BPD offers responded to from August 2015 to present. Each record includes the a date, latitude and longitude coordinates, and an offense code indicating the type of crime incident that occurred. I drop all crime incident records missing any of these three variables.

    \subsection{Census Tract Characteristics Data}
    I obtain time-invariant census tract level characteristics of the properties in my sample from Opportunity Insights \citep{chetty_impacts_2018}. This data includes information such as population density, job density, median household income, and poverty rate. Figure 2 plots the locations of the evictions in my sample, coloring Boston's census tracts according to their poverty rates. It shows that the density of eviction filings tends to be higher in poor areas. This result is consistent with existing research that finds strong associations between poverty and the prevalence of eviction \citep{desmond_housing_2016}. Indeed, 64 percent of eviction cases won by the plaintiff concern properties in census tracts with povery rates above 20 percent. This descriptive finding mirrors that of \cite{collinson_eviction_2022}: they show that 58 percent of evictions in New York and 46 percent of evictions in Cook County occur in census tracts with poverty rates above 20 percent.

            \begin{figure}[H]
            \centering
            \includegraphics[scale=1.3]{output/summary_statistics/figures/evictions_map.png}
            \caption{Spatial Incidence of Eviction}
            \label{fig:my_label}
        \end{figure}

@@

    Table 1 contains descriptive statistics for the panel dataset. \textcolor{red}{TODO}

@@

\section{Results and Potential Mechanisms} \label{sec:result}

    \subsection{Doubly Robust Estimates of the ATT}
    Doubly robust estimates of event-time aggregated treatment effects become negative and significantly different from zero during month two after treatment, and remain so for the next 34 months. \textcolor{red}{My identifying assumption of parallel trends between groups with the same pre-treatment characteristics appears satisfied; treatment effects at event times $-5$ through $-1$ are extremely close to 0. Treatment effects at event times $-6$ through $-1$ are not significantly different from 0.} Crime incident counts in the vicinity of treated properties and the vicinity of untreated properties only begin to change relative to each other after treatment occurs.

    Treatment effects from months 1 to 36 after treatment range from -1.54 to -4.94. The magnitudes of these point estimates are between 1.60 and 5.15 percent of the average number of crimes per month in a single property's radius in 2017

    the fact that they increase gradually during first three months after treatment is consistent with the fact that landlords have 90 days to file for execution.
    \begin{figure}[H]
        \centering
        \includegraphics{output/group_0_crimes_500m/figures/att_gt_dr_event_study_long_horizon.png}
        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters}
        \label{fig:my_label}
    \end{figure}

@@

    In this section, I argue that the most likely mechanism for the treatment effects I observe is the removal of targets of, accessories to, and/or culprits of crime incidents from the immediate vicinity of the property. Three pieces of evidence support this hypothesis.

    First, the steady increase in estimated treatment effects during the first three months after treatment is consistent with the timeline by which tenants are removed from properties. During months 0, 1, 2, and 3 relative to treatment, the magnitude of treatment effects steadily increases. This steady increase in estimated treatment effects during the first three months after treatment is consistent with the fact that an execution for possession remains valid for 90 days after its issuance and suggests that progressively more tenants are removed from units during the first three months after treatment. In contrast, treatment effect magnitudes at event times 4 and greater do not follow any clear pattern.

    Second, treatment effects are driven by evictions that were concluded during warm months. Post-treatment impacts of eviction are uniformly smaller in magnitude during cold months and largely insignificant from 0, as shown in Figures 4 and 5.

    Third, placebo tests using \<crimes that are most common in wealthy areas\> as an outcome do not show evidence

    1. placebo test

    2. warm results

    3. Steady increase

    Point estimates of the post-treatment $ATT(e)$'s become negative and significantly different from zero almost immediately after treatment and remain so for the next three years. Assuming that the units in my sample are vacant for less than three years after eviction, this means that treatment effects are negative both while the property is vacant and once a new tenant arrives.

    This suggests two things about evicted tenants. First, it suggests that just before eviction, they are culprits of, accessories to, or targets of crime incidents.

    Point estimates of the post-treatment ATT remain negative and significantly different from zero not just for the first few months after treatment, but for the first three years after treatment.

    \subsection{Robustness}
    \subsection{How does the lack of execution data bias my results?}
